An elaborate data set on human gait and the effect of mechanical perturbations

### 2014-12-09 paper.tex
Closes #34, abstract improved.

  Herein we share a typical gait data set collected from 11 subjects walking at
  a three speeds on an instrumented treadmill while being longitudinally
  perturbed during each stance phase with pseudo-random fluctuations in the
  speed of the treadmill belt. We provide raw marker and ground reaction loads in addition
  to a presentation of processed data that includes gait landmarks, 2D joint
  angles, angular rates, and joint torques and the software that does the
  processing. The protocol is described in detail along with the additional
  meta data about each of the data files. This data can be useful for
  validating or generating mathematical models that capable of simulating
  non-periodic and perturbed gaits.

>>>>

  Here we share a rich gait data set collected from fifteen subjects walking at
  three speeds on an instrumented treadmill. Each trial consists of 120 seconds
  of normal walking and 480 seconds of walking while being longitudinally
  and/or laterally perturbed during each stance phase with pseudo-random
  fluctuations in the speed of the treadmill belt. A total of approximately 1.5
  hours of normal walking ($>5000$ gait cycles) and 6 hours of perturbed walking
  ($>20,000$ gait cycles) is included in the data set. We provide raw marker
  locations and ground reaction loads in addition to a presentation of
  processed data that includes gait landmarks, 2D joint angles, angular rates,
  and joint torques and the software used for the computations. The protocol is
  described in detail along with additional elaborate meta data. This data can
  likely be useful for validating or generating mathematical models that are
  capable of simulating normal periodic gait and non-periodic, perturbed gaits.
